Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-02-03 manuscript.tex
Add moment of inertia

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.

>>>>

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.

The inertia tensor/matrix of a rigid body is defined~\cite{greenwood1988} as
\begin{align}\label{eq:moi_definition}
    J_I = \int_{\mathcal{B}} \bracket{ \parenth{\brho{}^T \brho{} }I - \brho{}\brho{}^T} dm, 
\end{align}
where \( \vc{\rho} \in \R^3 \) is the position of a mass element \( dm \) in the body fixed frame of the spacecraft.
One can also use~\cref{eq:xTx} to define the inertia matrix in several other equivalent forms
\begin{align*}
    J_I &= \int_{\mathcal{B}} \bracket{ \parenth{\vc{\rho}^T \vc{\rho} }I - \vc{\rho}\vc{\rho}^T} dm, \\
        &= \int_{\mathcal{B}} \tr{\vc{\rho}\vc{\rho}^T} I - \vc{\rho}\vc{\rho}^T, \\
        &= \int_{\mathcal{B}} \vh{\rho}^T \vh{\rho} dm.
\end{align*}
The location of an infinitesimal mass element \( dm \) can be decomposed into
\begin{align}\label{eq:mass_element_position}
    \vc{\rho}_i = \vc{\zeta} + \vc{\eta}_i, 
\end{align}
where \( \vc{\zeta} \) is the location of the center of \( m_i \) in the spacecraft fixed frame while \( \vc{\eta} \) the position of \( dm \) with respect to the center of \( m_i \) and expressed in the spacecraft fixed frame.
\Cref{fig:dumbbell_sc} shows the configuration of the vectors \( \vc{\zeta}, \vc{\eta} \) in the spacecraft fixed frame.
Using~\cref{eq:mass_element_position}, the moment of inertia can be expanded as
\begin{align*}
    J_I &= \sum_i^n \int_{\mathcal{B}_i} \parenth{\vc{\zeta}_i + \vc{\eta}_i}^T \parenth{\vc{\zeta}_i + \vc{\eta}_i } I  - \parenth{\vc{\zeta}_i + \vc{\eta}_i} \parenth{\vc{\zeta}_i + \vc{\eta}_i}^T dm .
\end{align*}
Expanding the product terms leads to
\begin{align*}
    J_I = \sum_i^n \int_{\mathcal{B}_i} \parenth{\vc{\zeta}_i^T \vc{\zeta}_i}I - \vc{\zeta}_i \vc{\zeta}_i^T + \vc{\eta}_i^T \vc{\eta}_i I - \vc{\eta}_i \vc{\eta}_i^T dm.
\end{align*}
Since the cross terms include an integration over the constant density sphere, the terms of the form
\begin{align*}
    \int_{\mathcal{B}_i} \vc{\eta}_i dm = 0,
\end{align*}
all become zero.
The integration is now split into two components: an integration within each sphere consisting of \( \vc{\eta}_i \) terms and an integration involving the location of the sphere in the spacecraft fixed frame consisting of \( \vc{\zeta}_i \) terms.
As a result, the final moment of inertia of a system of rigid spherical masses is 
\begin{align}\label{eq:dumbbell_moment_of_inertia}
    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
\end{align}
where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
\begin{align}\label{eq:sphere_moment_of_inertia}
    J_i = \begin{bmatrix} 
        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
        0 & \frac{2}{5} m_i r_i^2 & 0 \\
        0 & 0 & \frac{2}{5} m_i r_i^2 
    \end{bmatrix}.
\end{align}
\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.

\paragraph{Nonstandard Moment of Inertia}\label{sec:nonstandard_moi}
The standard moment of inertia \( J \in \R^{3 \times 3} \) of a rigid body is given by
\begin{align}\label{eq:standard_moment_of_inertia}
    J = \int_{\mathcal{B}} \vh{\rho}^T \vh{\rho} dm 
    = \int_{\mathcal{B}}  
    \begin{bmatrix} 
        y^2 + z^2 & -xy & -zx \\
        -xy & z^2 + x^2 & -yz \\
        -zx & yz & x^2 + y^2
    \end{bmatrix} dm, 
\end{align}
where \( \vc{\rho} = \begin{bmatrix} x & y & z \end{bmatrix}^T\) and defines the position of the mass element \( dm \) in the body fixed frame.
A nonstandard moment of inertia matrix \( J_d \in \R^{3 \times 3 } \) is defined as
\begin{align} \label{eq:nonstandard_moment_of_inertia}
    J_d = \int_{\mathcal{B}} \vc{\rho} \vc{\rho}^T dm = \int_{\mathcal{B}} 
    \begin{bmatrix}
        x^2 & xy & zx \\
        xy & y^2 & yz \\
        zx & yz & z^2
    \end{bmatrix} dm.
\end{align}
Using~\cref{eq:xTx} and the properties of the outer product, it can be shown that
\begin{subequations}\label{eq:moi_transformation}
    \begin{align}
        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
    \end{align}
\end{subequations}     
In addition, the following equation is also satisfied for any \( \vc{\Omega} \in \R^3 \)
\begin{align}\label{eq:moi_hat_prop}
    \parenth{J \vc{\Omega}}^\wedge = \vh{\Omega} J_d + J_d \vh{\Omega}.
\end{align}
\Cref{eq:moi_hat_prop} is easy to prove by substituting \( \vc{\Omega} = \begin{bmatrix} \Omega_1 & \Omega_2 & \Omega_3 \end{bmatrix}^T \) and expanding both sides of~\cref{eq:moi_hat_prop} to
\begin{align*}
    \begin{bmatrix}
        \parenth{J_{yy} + J_{zz}} \Omega_1 - J_{xy} \Omega_2 - J_{zx} \Omega_3 \\
        -J_{xy}\Omega_1 + \parenth{J_{zz} + J_{xx}} \Omega_2 - J_{yz}\Omega_3 \\
        -J_{zx}\Omega_1 - J_{yz}\Omega_2 + \parenth{J_{xx} + J_{yy}} \Omega_3
    \end{bmatrix}^\wedge,
\end{align*}
where \( J_{xy} = \int_{\mathcal{B}} xy dm \in \R \) and the other terms are defined similarly.

The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.

% TODO add definition of the moment of inertia tensor
